Predicting the 2024 U.S. Presidential Election: A Data-Driven Analysis of Swing State Outcomes

### 2024-11-04 paper/paper.qmd
new title

---
title: "Election 2024"
author: "Alexander Guarasci & Jacob Gilbert"
date: today
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This paper develops a predictive model for the 2024 U.S. Presidential Election, analyzing state-level polling data to forecast outcomes between Donald Trump and Kamala Harris. Using logistic regression, the model estimates the likelihood of Trump’s success in swing states by weighting polls based on recency and sample size. Findings indicate that Harris has a higher probability of winning in most swing states, though close margins suggest targeted campaign efforts could alter outcomes in pivotal areas. This analysis provides insight into electoral dynamics, highlighting how data-driven approaches can clarify potential election outcomes and inform strategic political decision-making.
---

@@

The Random contact method in which people are contacted does not provide random sampling, as non-response has made this method on its own more redundant. (@bailey2023new). This is clearly a factor here as the response rate was below 2%. The inclusion of response rate adjustments accounts for the likelihood that certain groups are more or less likely to respond to surveys, and is an efficient way to counter these issues (@Brick2013Nonresponse). The stratification also allows for a more representative expectation from the poll ensuring all significant groups are accurately represented in the sample as they are in the population (@Kish1965Survey), Making the means generated more accurate.

>>>>

---
title: "Predicting the 2024 U.S. Presidential Election: A Data-Driven Analysis of Swing State Outcomes"
subtitle: "Forecast Model Suggests Harris as the Probable Winner of the majority of swing states"
author: "Alexander Guarasci & Jacob Gilbert"
date: today
date-format: long
bibliography: references.bib
execute:
  echo: false
format: pdf
fig-pos: "H"
abstract: |
 This paper develops a predictive model for the 2024 U.S. Presidential Election, analyzing state-level polling data to forecast outcomes between Donald Trump and Kamala Harris. Using logistic regression, the model estimates the likelihood of Trump’s success in swing states by weighting polls based on recency and sample size. Findings indicate that Harris has a higher probability of winning in most swing states, though close margins suggest targeted campaign efforts could alter outcomes in pivotal areas. This analysis provides insight into electoral dynamics, highlighting how data-driven approaches can clarify potential election outcomes and inform strategic political decision-making.
---

@@

The Random contact method in which people are contacted does not provide random sampling, as non-response has made this method on its own more redundant. (@bailey2023new). This is clearly a factor here as the response rate was below 2%. The inclusion of response rate adjustments accounts for the likelihood that certain groups are more or less likely to respond to surveys, and is an efficient way to counter these issues (@brick2013Nonresponse). The stratification also allows for a more representative expectation from the poll ensuring all significant groups are accurately represented in the sample as they are in the population (@Kish1965Survey), Making the means generated more accurate.
